Supplementary material to: Empirical Bayes estimation of the normal inverse Gaussian prior in simultaneous-equation models

### 2019-07-29 docs/manuscript1.Rnw
testing enig on gdsc data

  \section{Extended model II}
  We propose a second extension of model (\ref{eq:priormodel}) 
  that incorporates co-data $\mathbf{c}_{d}^j$ that describes the relationship
  between covariate $j$ and outcome $d$, collected in
  $\mathbf{C} = \begin{bmatrix} \mathbf{c}_{1}^1 & \cdots & \mathbf{c}_{1}^p &
  \cdots & \mathbf{c}_{D}^1 & \cdots & \mathbf{c}_{D}^p
  \end{bmatrix}_{1 \times pD} \tr$. An example from eQTL is the 
  distance between SNP and gene. Model (\ref{eq:priormodel}) is then rewritten
  as:
  \begin{subequations}\label{eq:extendedmodel2}
    \begin{align*}
      y_{id} | \bm{\beta}_d, \sigma_d^2 & \sim \mathcal{N} 
      \(\x_i \tr \bm{\beta}_d, \sigma_d^2\), \nonumber \\
      \beta_{jd} | \gamma_{jd}^2, \sigma_d^2 & \sim \mathcal{N} 
      \(0, \sigma_d^2 \gamma_{jd}^2 \), \\
      \gamma_{jd}^2 & \sim \mathcal{IG}
      \( [(\mathbf{c}_{d}^j) \tr \bm{\alpha}]^{-1}, \lambda_{d} \), \\
      \sigma_d^2 & \sim 1/\sigma_d^3, \nonumber
    \end{align*}
  \end{subequations}
  where now the variance components $\gamma_{jd}^2$ are both outcome and 
  covariate specific and modelled as a function of the co-data 
  $\mathbf{c}_{d}^j$. We will
  refer to this model as the extended normal
  inverse Gaussian (ENIG) model
  The formulation as in (\ref{eq:extendedmodel2}) results in the following
  variational distribution for the $\gamma^2_{jd}$:
  $$
  q(\gamma_{jd}^2) \overset{D}{=} \mathcal{GIG}
  \(-1, \lambda_{d}[(\mathbf{c}_{d}^j) \tr \bm{\alpha}]^2, \delta_{jd}\).
  $$
  The variational parameters are iteratively updated by:
  \begin{align*}
    \bm{\Sigma}_d^{(h+1)} & = (a_d^{(h)})^{-1} 
    \[\X \tr \X + \diag(b_{jd}^{(h)})\]^{-1}, \\
    \bm{\mu}_d^{(h+1)} & = \[\X \tr \X + \diag(b_{jd}^{(h)})\]^{-1} 
    \X \tr \y_d, \\
    \delta_{jd}^{(h+1)} & = a_d^{(h)} \[(\bmu^{(h+1)}_{jd})^2 + 
    (\bSigma_d)_{jj}\] + \lambda_{d}, \\ 
    \zeta_d^{(h+1)} & = \frac{1}{2} \bigg[\mathbf{y}_d \tr \mathbf{y}_d -
    2 \mathbf{y}_d \tr \X \bm{\mu}_d^{(h+1)} + 
    \trace ( \X \tr \X \bm{\Sigma}_d^{(h+1)}) + 
    (\bm{\mu}_d^{(h+1)}) \tr \X \tr \X \bm{\mu}_d^{(h+1)} \\
    & \,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\, + 
    \trace \[ \diag (b_{jd}^{(h+1)}) \bm{\Sigma}_d^{(h+1)}\] + 
    (\bm{\mu}_d^{(h+1)}) \tr \diag (b_{jd}^{(h+1)}) 
    \bm{\mu}_d^{(h+1)}\bigg],
  \end{align*}
  until convergence, where
  $$
  b_{jd}^{(h)}=\sqrt{\frac{\delta_{jd}^{(h)}}
  {\lambda_{d}[(\mathbf{c}_{d}^j) \tr \bm{\alpha}]^2}}
  \frac{K_0(\sqrt{\delta_{jd}^{(h)}\lambda_{d}}
  [(\mathbf{c}_{d}^j) \tr \bm{\alpha}])}
  {K_1(\sqrt{\delta_{jd}^{(h)}\lambda_{d}}
  [(\mathbf{c}_{d}^j) \tr \bm{\alpha}])} + 
  \frac{2}{\delta_{jd}^{(h)}}.
  $$ 
  The empirical Bayes step consists of an iteratively 
  reweighted least squares regression with iterations:
  \begin{align*}
    \bm{\alpha} & = \[ \mathbf{C} \tr \bLambda \diag 
    (e_{jd}^{(l)}) \mathbf{C} \]^{-1} \mathbf{C} \tr \bLambda
    \mathbf{1}_{pD \times 1}, \\
    \lambda_{d} & = p \left\{ \sum_{j=1}^p b_{jd}^{(l)} + 
    \sum_{j=1}^p e_{jd}^{(l)} [(\mathbf{c}_{d}^j) \tr \bm{\alpha}]^2 - 
    2 \sum_{j=1}^p (\mathbf{c}_{d}^j) \tr \bm{\alpha} \right\}^{-1},
  \end{align*}
  where $\bLambda=\I_p \otimes \diag(\lambda_d)$ and 
  $e_{jd}^{(l)} = (b_{jd}^{(l)} - 
  2/\delta_{jd}^{(l)}) \cdot \delta_{jd}^{(l)}/[\lambda_{d}^{(l)}
  \left\{(\mathbf{c}_{d}^j) \tr \bm{\alpha}]^2\right\}$.

@@

  \section{Simulations}
  \subsection{Comparison of priors}
  \label{sec:inversegammamodel}
  A common default prior for latent variance components is the inverse Gamma
  prior:
  $$
  \gamma_d^2 \sim \Gamma^{-1}(\eta_d/2,\lambda_d/2),
  $$
  with shape $\eta_d/2$ and scale $\lambda_d/2$, both rescaled to match our 
  inverse Gaussian prior formulation. The resulting marginal prior for the model
  parameters
  (conditional on the error variance $\sigma_d^2$) is then a scaled Student's 
  $t$-distribution:
  $$
  \beta_j | \sigma_d^2 \sim \text{Student's } 
  t\(\eta_d,\sigma_d \sqrt{\lambda_d/\eta_d}\),
  $$
  with degrees of freedom $\eta_d$ and scale $\sigma_d \sqrt{\lambda_d/\eta_d}$.
  See SM Section \ref{sm-sec:inversegamma} for more details on this prior. 
  We compare the 
  posteriors of the proposed NIG, DNIG, and EGIG priors to the scaled Student's 
  $t$-distribution prior in a simulated setting.

@@

  In the sparse setting, the observed data generating process is the same. The
  model parameters are are simulated from a spike-and-slab prior with a 
  Gaussian slab:
  \begin{align*}
    w & \sim \text{Beta}(\nu, \kappa), \\
    z_j | w & \sim \text{Binom}(w), \\
    \beta_j | z_j & \sim z_j \mathcal{N} \( 0, 1\) +
    (1 - z_j)\delta_0,
  \end{align*}
  where $\delta_0$ denotes the Dirac mass at zero. The slab is chosen
  such that the we have marginal prior variance $\V(\beta_j)=1$. The sparsity 
  level is determined by the proportion of zero $\beta_j$, 
  $s=1 - \nu/(\nu + \kappa)$. Note that the resulting marginal prior for
  $\beta_j$ is:
  $$
  \beta_j \sim (s - 1)\mathcal{N} \( 0, 1\) + s\delta_0.
  $$
  We use two settings, $s=0.5$ and $s=0.9$. The 
  hyperparameters for estimation are set the same as in the dense setting, 
  resulting in a total of 12 different simulation settings.
  To mitigate the effect of random variation, we
  repeated the simulations 100 times and report the results in Figures 
  [! ref to figure here]

@@

  \section{Empirical Bayes estimation}
  We simulate from a correctly specified model given in \ref{eq:priormodel}. We 
  assume random $y_{id}$, $\x_i$, and $\bm{\beta}_d$, while we fix $\mathbf{C}$,
  $\gamma_d^2$, $\sigma_d^2$ and $\bm{\alpha}$. We estimate the $\bm{\mu}_d$,
  $\bm{\Sigma}_d$, $\delta_d$, $\bm{\alpha}$ and $\lambda$, while we fix the
  $\sigma_d^2$ to their true values.

@@

  \section{Application}
  - Possible: network reconstruction, medical surveys, drug response prediction

  - metabolomics data: oxidative stress als uitkomst van de andere metabolieten
  min organic acids omdat ze downstream zijn. oxidateve stress onderverdelen in
  high and low als uitkomst co-data en de andere metabolieten onderverdelen
  als predictor co-data.
  \section{Discussion}
  - inverse Gaussian more convenient than inverse Gamma, because EB is closed-
  form

@@

>>>>

  \section{Extended model II}
  We propose a second extension of model (\ref{eq:priormodel}) 
  that incorporates co-data $\mathbf{c}_{d}^j$ that describes the relationship
  between covariate $j$ and outcome $d$, collected in
  $\mathbf{C} = \begin{bmatrix} \mathbf{c}_{1}^1 & \cdots & \mathbf{c}_{1}^p &
  \cdots & \mathbf{c}_{D}^1 & \cdots & \mathbf{c}_{D}^p
  \end{bmatrix}_{|\bm{\alpha}| \times pD} \tr$. An example from eQTL is the 
  distance between SNP and gene. Model (\ref{eq:priormodel}) is then rewritten
  as:
  \begin{subequations}\label{eq:extendedmodel2}
    \begin{align*}
      y_{id} | \bm{\beta}_d, \sigma_d^2 & \sim \mathcal{N} 
      \(\x_i \tr \bm{\beta}_d, \sigma_d^2\), \nonumber \\
      \beta_{jd} | \gamma_{jd}^2, \sigma_d^2 & \sim \mathcal{N} 
      \(0, \sigma_d^2 \gamma_{jd}^2 \), \\
      \gamma_{jd}^2 & \sim \mathcal{IG}
      \( [(\mathbf{c}_{d}^j) \tr \bm{\alpha}]^{-1}, \lambda_{d} \), \\
      \sigma_d^2 & \sim 1/\sigma_d^3, \nonumber
    \end{align*}
  \end{subequations}
  where now the variance components $\gamma_{jd}^2$ are both outcome and 
  covariate specific and modelled as a function of the co-data 
  $\mathbf{c}_{d}^j$. We will
  refer to this model as the extended normal
  inverse Gaussian (ENIG) model
  The formulation as in (\ref{eq:extendedmodel2}) results in the following
  variational distribution for the $\gamma^2_{jd}$:
  $$
  q(\gamma_{jd}^2) \overset{D}{=} \mathcal{GIG}
  \(-1, \lambda_{d}[(\mathbf{c}_{d}^j) \tr \bm{\alpha}]^2, \delta_{jd}\).
  $$
  The variational parameters are iteratively updated by:
  \begin{align*}
    \bm{\Sigma}_d^{(h+1)} & = (a_d^{(h)})^{-1} 
    \[\X \tr \X + \diag(b_{jd}^{(h)})\]^{-1}, \\
    \bm{\mu}_d^{(h+1)} & = \[\X \tr \X + \diag(b_{jd}^{(h)})\]^{-1} 
    \X \tr \y_d, \\
    \delta_{jd}^{(h+1)} & = a_d^{(h)} \[(\bmu^{(h+1)}_{jd})^2 + 
    (\bSigma_d)_{jj}\] + \lambda_{d}, \\ 
    \zeta_d^{(h+1)} & = \frac{1}{2} \bigg[\mathbf{y}_d \tr \mathbf{y}_d -
    2 \mathbf{y}_d \tr \X \bm{\mu}_d^{(h+1)} + 
    \trace ( \X \tr \X \bm{\Sigma}_d^{(h+1)}) + 
    (\bm{\mu}_d^{(h+1)}) \tr \X \tr \X \bm{\mu}_d^{(h+1)} \\
    & \,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\, + 
    \trace \[ \diag (b_{jd}^{(h+1)}) \bm{\Sigma}_d^{(h+1)}\] + 
    (\bm{\mu}_d^{(h+1)}) \tr \diag (b_{jd}^{(h+1)}) 
    \bm{\mu}_d^{(h+1)}\bigg],
  \end{align*}
  until convergence, where
  $$
  b_{jd}^{(h)}=\sqrt{\frac{\delta_{jd}^{(h)}}
  {\lambda_{d}[(\mathbf{c}_{d}^j) \tr \bm{\alpha}]^2}}
  \frac{K_0(\sqrt{\delta_{jd}^{(h)}\lambda_{d}}
  [(\mathbf{c}_{d}^j) \tr \bm{\alpha}])}
  {K_1(\sqrt{\delta_{jd}^{(h)}\lambda_{d}}
  [(\mathbf{c}_{d}^j) \tr \bm{\alpha}])} + 
  \frac{2}{\delta_{jd}^{(h)}}.
  $$ 
  The empirical Bayes step consists of an iteratively 
  reweighted least squares regression with iterations:
  \begin{align*}
    \bm{\alpha} & = \[ \mathbf{C} \tr \bLambda \diag 
    (e_{jd}^{(l)}) \mathbf{C} \]^{-1} \mathbf{C} \tr \bLambda
    \mathbf{1}_{pD \times 1}, \\
    \lambda_{d} & = p \left\{ \sum_{j=1}^p b_{jd}^{(l)} + 
    \sum_{j=1}^p e_{jd}^{(l)} [(\mathbf{c}_{d}^j) \tr \bm{\alpha}]^2 - 
    2 \sum_{j=1}^p (\mathbf{c}_{d}^j) \tr \bm{\alpha} \right\}^{-1},
  \end{align*}
  where $\bLambda=\I_p \otimes \diag(\lambda_d)$ and 
  $e_{jd}^{(l)} = (b_{jd}^{(l)} - 
  2/\delta_{jd}^{(l)}) \cdot \delta_{jd}^{(l)}/[\lambda_{d}^{(l)}
  \left\{(\mathbf{c}_{d}^j) \tr \bm{\alpha}]^2\right\}$.

@@

  \section{Simulations}
  Our simulation study consists of three parts investigating the model and its
  estimation:
  \begin{enumerate}
    \item Prior performance
    \item Variational Bayes approximation
    \item Empirical Bayes estimation
  \end{enumerate}

  \subsection{Comparison of priors}
  \label{sec:inversegammamodel}
  A common default prior for latent variance components is the inverse Gamma
  prior:
  $$
  \gamma_d^2 \sim \Gamma^{-1}(\eta_d/2,\xi_d/2),
  $$
  with shape $\eta_d/2$ and scale $\xi_d/2$, both rescaled to match our 
  inverse Gaussian prior formulation. The resulting marginal prior for the model
  parameters
  (conditional on the error variance $\sigma_d^2$) is then a scaled Student's 
  $t$-distribution:
  $$
  \beta_j | \sigma_d^2 \sim \text{Student's } 
  t\(\eta_d,\sigma_d \sqrt{\xi_d/\eta_d}\),
  $$
  with degrees of freedom $\eta_d$ and scale $\sigma_d \sqrt{\xi_d/\eta_d}$.
  See SM Section \ref{sm-sec:inversegamma} for more details on this prior. 
  We compare the 
  posteriors of the proposed NIG, DNIG, and EGIG priors to the scaled Student's 
  $t$-distribution prior in a simulated setting.

@@

  In the sparse setting, the observed data generating process is the same. The
  model parameters are are simulated from a spike-and-slab prior with both the
  spike and slab Gaussian:
  \begin{align*}
    w & \sim \text{Beta}(\phi, \chi), \\
    z_j | w & \sim \text{Bernoulli}(w), \\
    \beta_j | z_j & \sim z_j \mathcal{N} \( 0, 1 + 0.99 \frac{\chi}{\phi}\) +
    (1 - z_j)\mathcal{N} \( 0, 0.01\).
  \end{align*}
  The slab is chosen
  such that the we have marginal prior variance $\V(\beta_j)=1$. The sparsity 
  level is determined by the proportion of zero $\beta_j$, 
  $s=1 - \phi/(\phi + \chi)$. Note that the resulting marginal prior for
  $\beta_j$ is:
  $$
  \beta_j \sim (1 - s)\mathcal{N} \( 0, \frac{1 - 0.01 s}{1 - s}\) + 
  s \mathcal{N} \( 0, 0.01\).
  $$
  We use two settings, $s=0.5$ and $s=0.9$. The 
  hyperparameters for estimation are set the same as in the dense setting, 
  resulting in a total of 12 different simulation settings 
  (6 per sparsity setting).
  To mitigate the effect of random variation, we
  repeated the simulations 100 times and report the results in Figures 
  [! ref to figure here]

@@

  \subsection{Empirical Bayes estimation}
  We simulate from a correctly specified model given in \ref{eq:priormodel}. We 
  assume random $y_{id}$, $\x_i$, and $\bm{\beta}_d$, while we fix $\mathbf{C}$,
  $\gamma_d^2$, $\sigma_d^2$ and $\bm{\alpha}$. We estimate the $\bm{\mu}_d$,
  $\bm{\Sigma}_d$, $\delta_d$, $\bm{\alpha}$ and $\lambda$, while we fix the
  $\sigma_d^2$ to their true values.

@@

  \section{Application in eQTL detection}
  - Genes from p38MAPK pathway. Possible co-data are:
  \begin{itemize}
    \item gene $\times$ SNP: distance of SNP to gene (continuous)
    \item gene: length of the gene (continuous) 
      (and possibly chromosome number (categorical))
    \item SNP: within or outside of gene (binary), intron or exon (binary),
      and minor allele frequency (continuous)
  \end{itemize}
  Within or outside of gene and distance of SNP to gene are probably highly
  collinear.

  From Gino: 108 Geuvadis genes, 9 removed because they contained just one 
  subject. Annotation is from GRCh37 reference genome: 
  \url{https://www.ncbi.nlm.nih.gov/assembly/GCF_000001405.13/}. 
  Annotation file that Gino used: 
  \url{https://www.gencodegenes.org/human/release_12.html}.
  Ensembl version of this genome:
  \url{https://grch37.ensembl.org/Homo_sapiens/Info/Index}.
  Possibly use GeuvadisTranscriptExpr R package.

  - compare to intercept only co-data model, i.e., 
  $\mathbf{C} = \mathbf{1}_{pD \times 1}$.

  - show influence of co-data with standardized $\bm{\alpha}$'s.

  - comparison in terms of explained heritability by plotting explained 
  heritability versus number of SNPs used to calculate explained heritability,
  where explained heritability is fraction of heritability explained with top 
  SNPs and heritability explained with all SNPs. We may calculate the AUC of
  this curve to quantify performance in one number per regression.

  The posterior mean of the heritability is approximated by 
  \begin{align*}
    \E(h_d^2 | \y_d) & = \E \( \frac{\sigma^2_d \sum_{j=1}^{p_d} 
    \gamma_{jd}^2}{\sigma^2_d \sum_{j=1}^{p_d} \gamma_{jd}^2 + 
    \sigma_d^2} \bigg| \y_d \) 
    \approx \E_Q \( \frac{\sum_{j=1}^{p_d} \gamma_{jd}^2}
    {\sum_{j=1}^{p_d} \gamma_{jd}^2 + 1} \) \\
    & \approx \frac{\sum_{j=1}^{p_d} \E_Q (\gamma_{jd}^2)}
    {\sum_{j=1}^{p_d} \E_Q (\gamma_{jd}^2) + 1} - 
    \frac{\sum_{j=1}^{p_d} \V_Q (\gamma_{jd}^2)}
    {\[\sum_{j=1}^{p_d} \E_Q (\gamma_{jd}^2) + 1\]^3},
  \end{align*}
  where the last step is the result of a second order Taylor approximation.

  Also compare by log pseudo marginal likelihood 
  $LPML_d = n^{-1}\sum_{i=1}^n \log (CPO_{id})$ \cite[]{gelfand_model_1992}. Let 
  $\theta_{id}=\x_i \tr \bbeta_d$. Then the conditional 
  predictive ordinates (CPO) are given by:
  \begin{align*}
    CPO_{id} & = p(\y_{id} | \y_{-id}) = \int_{-\infty}^{\infty} \int_0^{\infty}
    p(\y_{id} | \bbeta_d, \sigma_d^2 ) \pi (\bbeta | \y_{-id}, \sigma_d^2) 
    \pi (\sigma_d^2 | \y_{-id}) d\sigma_d^2 d\bbeta_d \\
    & = \int_{-\infty}^{\infty} \int_0^{\infty}
    p(\y_{id} | \theta_{id}, \sigma_d^2 ) 
    \pi (\theta_{id} | \y_{-id}, \sigma_d^2) 
    \pi (\sigma_d^2 | \y_{-id}) d\sigma_d^2 d\theta_{id},
  \end{align*}
  where
  \begin{align*}
    \y_i | \theta_{id}, \sigma_d^2 & \sim \mathcal{N} (\theta_{id}, 
    \sigma_d^2), \\
    \theta_{id} | \y_{-id} & \sim \mathcal{N}(\x_i \tr \bmu_{-id}, 
    \x_i \tr \bSigma_{-id} \x_i), \\
    \sigma_d^2 | \y_{-id} & \sim \Gamma^{-1} \( \frac{n - n_{id} + p + 1}{2},
    \zeta_{-id} \),
  \end{align*}
  $n_{id}$ denotes the number of elements in $\y_{id}$ and $\bmu_{-id}$, 
  $\bSigma_{-id}$, and $\zeta_{-id}$ are the corresponding parameters estimated
  from $\y_{-id}$. Plugging in the densities we see that we have:
  \begin{align*}
    CPO_{id} = & (2 \pi)^{-1} \frac{\Gamma\(\frac{n - n_{id} + p + 2}{2}\)}
    {\Gamma\(\frac{n - n_{id} + p + 1}{2}\)}
    (\zeta_{-id} \x_i \tr \bSigma_{-id} \x_i)^{-1/2} \\
    & \cdot \int_{-\infty}^{\infty}
    \( \frac{\theta^2}{2\zeta_{-id}} + 1 \)^{-\frac{n - n_{id} + p + 2}{2}}
    \exp \[ - \frac{(\theta - \x_i \tr \bmu_{-id} + y_i)^2}
    {2 \x_i \tr \bSigma_{-id} \x_i} \] d\theta,
  \end{align*}
  a one-dimensional (well-behaved) integral that is easily solved with some 
  numerical integration routine

  - Also possible: network reconstruction, medical surveys, drug response 
  prediction, metabolomics data: oxidative stress als uitkomst van de andere 
  metabolieten
  min organic acids omdat ze downstream zijn. oxidateve stress onderverdelen in
  high and low als uitkomst co-data en de andere metabolieten onderverdelen
  als predictor co-data.

  \section{Discussion}
  - inverse Gaussian more convenient than inverse Gamma, because EB is closed-
  form

@@

  - issues: co-data needs to be positive

### 2019-07-29 docs/manuscript2.Rnw
testing enig on gdsc data

>>>>

	From Oslo:
	1.2) Preselecting GEX features: we selected gene expression features
explaining 50\% variations over all cell lines, since this results in not too
features and probably remains those important features.

1.3) Preselecting CNV: we used the same strategy as Garnett et al. (2012) where the GDSC data are from.

1.4) Preselecting MUT: we deleted mutated genes with less than two cell lines.

### 2019-07-29 docs/supplement1.Rnw
testing enig on gdsc data

	\section{NIG prior}\label{sec:nigprior}
	For a fixed error variance $\sigma_d^2$, we have a marginal prior variance 
	and kurtosis:
	\begin{align*}
	  \V(\beta_{jd} | \sigma_d^2) & = \sigma_d^2 \theta_d, \\
	  \mathcal{K}(\beta_{jd} | \sigma_d^2) & = \frac{3\theta_d}{\lambda_d} + 3.
	\end{align*}

	\section{NIGIG prior}\label{sec:dnigprior}
	Equivalently, we may set 
  $\eta_{jd}^2=\tau_j^2 \gamma_d^2/(\theta_j^z \theta_d^c)$ and write 
  MD equation (\ref{md-eq:extendedmodel1}) as:
  \begin{align*}
    \beta_{jd} | \eta_{jd}^2, \sigma_d^2 & \sim \mathcal{N} 
    \(0, \frac{\lambda_{jd}}{\chi_{jd}}\eta_{jd}^2\sigma_d^2\), \\
    \eta_{jd}^2 & \overset{D}{=}\pi^{-1}\sqrt{\chi_{jd}}\exp(\psi_{jd}) 
    \eta_{jd}^{-3/2} \cdot K_{0} \(\sqrt{\psi_{jd}^2 + \chi_{jd} (\eta_{jd}^2 
    + \eta_{jd}^{-2} - 2)} \),
  \end{align*}
  where $\lambda_{jd}=\lambda_j^z\lambda_d^c$, 
  $\chi_{jd}=\lambda_j^z\lambda_d^c/(\theta_j^z \theta_d^c)$, and
  $\psi_{jd}=\lambda_j^z/\theta_j^z + \lambda_d^c/ \theta_d^c$. A third way
  of writing the model is:
  \begin{subequations}\label{eq:extendedmodel1.2}
    \begin{align}
      \beta_{jd} | \eta_{jd}^2, \sigma_d^2 & \sim \mathcal{N} 
      \(0, \eta_{jd}^2 \sigma_d^2\), \\
      \eta_{jd}^2 | \xi_{d}^2 & \sim \mathcal{IG} 
      (\theta_j^z \xi_d^2, \lambda_j^z \xi_d^2 ), \\
      \xi_d^2 & \sim \mathcal{GIG} (1, \lambda_d^c/(\theta_d^c)^2, \lambda_d^c).
    \end{align}
  \end{subequations}
	From (\ref{eq:extendedmodel1.2}), for a fixed error variance
	$\sigma_d^2$, we find the marginal prior variance and kurtosis:
	\begin{subequations}\label{eq:varkurtdgig}
	  \begin{align}
	    \V(\beta_{jd} | \sigma_d^2) & = \sigma_d^2 \theta_d^c \theta_j^z  
      \(r_d + \frac{2\theta_d^c}{\lambda_d^c}\), \\
	    \mathcal{K}(\beta_{jd} | \sigma_d^2) & = \(\frac{3\theta_j^z}
	    {\lambda_j^z} + 3\) \frac{4 \theta_d^c (r_d + 2\theta_d^c/\lambda_d^c) +
	    1}{\lambda_d^c(r_d + 2\theta_d^c/\lambda_d^c)^2},
	  \end{align}
	\end{subequations}
	with $r_d = K_0(\lambda_d^c/\theta_d^c)/K_1(\lambda_d^c/\theta_d^c)$.
	If 
  we fix the prior expectation $\E(\gamma_d^2)=\theta_d^c$ and let the prior 
  variance 
  $\V(\gamma_d^2)$ go to zero, we have $\V(\beta_{jd} | \sigma_d^2) \rightarrow
  \sigma_d^2 \theta_j^z \theta_d^c$ and $\mathcal{K}(\beta_{jd} | \sigma_d^2)
  \rightarrow 3(\theta_j^z/\lambda_j^z + 1)$. From (\ref{eq:varkurtdgig}) we see
  that we can keep the variance constant by fixing $\theta_j^z$, $\theta_d^c$,
  and $\lambda_d^c$, while we increasing the kurtosis by decrearing 
  $\lambda_j^z$. This makes the model MD equations (\ref{md-eq:extendedmodel1})
  a flexible model.

>>>>

	\section{NIG and ENIG prior}\label{sec:nigprior}
	For a fixed error variance $\sigma_d^2$, we have a marginal prior variance 
	and kurtosis:
	\begin{align*}
	  \V(\beta_{jd} | \sigma_d^2) & = \sigma_d^2 \theta_d, \\
	  \mathcal{K}(\beta_{jd} | \sigma_d^2) & = \frac{3\theta_d}{\lambda_d} + 3.
	\end{align*}

	\section{DGIG prior}\label{sec:dnigprior}
	Equivalently, we may set 
  $\eta_{jd}^2=\tau_j^2 \gamma_d^2/(\theta_j^z \theta_d^c)$ and write 
  MD equation (\ref{md-eq:extendedmodel1}) as:
  \begin{align*}
    \beta_{jd} | \eta_{jd}^2, \sigma_d^2 & \sim \mathcal{N} 
    \(0, \frac{\lambda_{jd}}{\chi_{jd}}\eta_{jd}^2\sigma_d^2\), \\
    \eta_{jd}^2 & \overset{D}{=}\pi^{-1}\sqrt{\chi_{jd}}\exp(\psi_{jd}) 
    \eta_{jd}^{-3/2} \cdot K_{0} \(\sqrt{\psi_{jd}^2 + \chi_{jd} (\eta_{jd}^2 
    + \eta_{jd}^{-2} - 2)} \),
  \end{align*}
  where $\lambda_{jd}=\lambda_j^z\lambda_d^c$, 
  $\chi_{jd}=\lambda_j^z\lambda_d^c/(\theta_j^z \theta_d^c)$, and
  $\psi_{jd}=\lambda_j^z/\theta_j^z + \lambda_d^c/ \theta_d^c$. A third way
  of writing the model is:
  \begin{subequations}\label{eq:extendedmodel1.2}
    \begin{align}
      \beta_{jd} | \eta_{jd}^2, \sigma_d^2 & \sim \mathcal{N} 
      \(0, \eta_{jd}^2 \sigma_d^2\), \\
      \eta_{jd}^2 | \xi_{d}^2 & \sim \mathcal{IG} 
      (\theta_j^z \xi_d^2, \lambda_j^z \xi_d^2 ), \\
      \xi_d^2 & \sim \mathcal{GIG} (1, \lambda_d^c/(\theta_d^c)^2, \lambda_d^c).
    \end{align}
  \end{subequations}
	From (\ref{eq:extendedmodel1.2}), for a fixed error variance
	$\sigma_d^2$, we find the marginal prior variance and kurtosis:
	\begin{subequations}\label{eq:varkurtdgig}
	  \begin{align}
	    \V(\beta_{jd} | \sigma_d^2) & = \sigma_d^2 \theta_d^c \theta_j^z  
      \(r_d + \frac{2\theta_d^c}{\lambda_d^c}\), \\
	    \mathcal{K}(\beta_{jd} | \sigma_d^2) & = \(\frac{3\theta_j^z}
	    {\lambda_j^z} + 3\) \frac{4 \theta_d^c (r_d + 2\theta_d^c/\lambda_d^c) +
	    1}{\lambda_d^c(r_d + 2\theta_d^c/\lambda_d^c)^2},
	  \end{align}
	\end{subequations}
	with $r_d = K_0(\lambda_d^c/\theta_d^c)/K_1(\lambda_d^c/\theta_d^c)$.
	If 
  we fix the prior expectation $\E(\gamma_d^2)=\theta_d^c$ and let the prior 
  variance 
  $\V(\gamma_d^2)$ go to zero, we have $\V(\beta_{jd} | \sigma_d^2) \rightarrow
  \sigma_d^2 \theta_j^z \theta_d^c$ and $\mathcal{K}(\beta_{jd} | \sigma_d^2)
  \rightarrow 3(\theta_j^z/\lambda_j^z + 1)$. From (\ref{eq:varkurtdgig}) we see
  that we can keep the variance constant by fixing $\theta_j^z$, $\theta_d^c$,
  and $\lambda_d^c$, while we increasing the kurtosis by decrearing 
  $\lambda_j^z$. This makes the model MD equations (\ref{md-eq:extendedmodel1})
  a flexible model.
